Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-23 bdcloud_paper/latex/paper.tex
Edited HMM equations

The proposed transaction time is found from the exhaustion times (Eq.~\ref{eq:transaction-times}).  For each item category, the offset time $T_{O, i}$ between when a customer would visit the store and the exhaustion time is sampled from an exponential distribution parameterized separately for each customer $c$. A proposed transaction time $T_{P, i}$ for each item category is found by subtracting the offset time $T_{O, i}$ from the exhaustion time $T_{E, i}$.  The earliest proposed transaction time is taken as the overall proposed transaction time $T_T$. \textcolor{red}{$\beta_c$}

@@

\begin{equation*}
w_i = - \lambda_i \exp(-\lambda_i (T_{E, i}- T_{T}))
\end{equation*}

The item category for each purchase is chosen by sampling from the item categories with the probability of choosing each item category $i$ proportional to its weight $w_i$. \textcolor{red}{$\lambda_i$ - maybe these should be per customer / item category instead of just per item category}

@@

If the weights are greater than 1, they are rounded down to 1.  Likese, if the weights are less than 0, they are rounded up to 0.

>>>>

The proposed transaction time is found from the exhaustion times (Eq.~\ref{eq:transaction-times}).  For each item category, the offset time $T_{O, i}$ between when a customer would visit the store and the exhaustion time is sampled from an exponential distribution. The distribution is parameterized by $\beta_c$, the average number of days before triggering a transaction. The parameter $\beta_c$ is set separately for each customer $c$ by sampling from a uniform distribution. A proposed transaction time $T_{P, i}$ for each item category is found by subtracting the offset time $T_{O, i}$ from the exhaustion time $T_{E, i}$.  The earliest proposed transaction time is taken as the overall proposed transaction time $T_T$.

@@

\begin{align*}
&w_i = - \beta^{-1}_c \exp(-\beta^{-1}_c (T_{E, i}- T_T)) \\
&\beta^{-1}_c \sim U(a,b)
\end{align*}

where $\beta_c$ the average number of days between when a customer purchases an item and the exhaustion time. The value $\beta_c$ is set separately for each customer by sampling from a uniform distribution. The value $w_i$ is used to model the propensity for a customer to purchase an item they will run out at time $T_{E, i}$ in the future when at the store at time $T_T$.

The item category is chosen by sampling from the item categories with the probability of choosing each item category $i$ proportional to its weight $w_i$.

@@

If the weights are greater than 1, they are rounded down to 1.  Likewise, if the weights are less than 0, they are rounded up to 0.
